### 2016-01-07 pdocs/thesis/introduction.tex
pdocs

\subsection{Physics engines}

>>>>

\begin{tikzpicture}
  \begin{scope}[blend group = soft light]
    \fill[red!30!white]   ( 90:3.2) circle (5);
    \fill[green!30!white] (210:3.2) circle (5);
    \fill[blue!30!white]  (330:3.2) circle (5);
  \end{scope}
  \node at ( 90:4)   [align=left] {structural analysis\\
material plasticity};
  \node at ( 210:4)   [align=left] {physics engine\\
rigid bodies\\
constraints};
  \node at ( 330:4)   [align=left] {programming\\
extending of bulletphysics\\
verification
};
  \node {\begin{varwidth}{2cm}plasticity in constraints\end{varwidth}};
\end{tikzpicture}

\subsection{Physics engine}
